Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-16 WSSSPE3/report/wg_main_user_community.tex
adding cite for mozilla working open guide

Mozilla Science maintains a ``Working Open Project Guide'' (\url{http://mozillascience.github.io/leadership-training}), the introduction of which states: \katznote{should get changed to a cite}
\begin{quote}
Working openly with contributors enables your
    community to learn how to build and collaborate together. This
    document is a guideline on how to work openly and involve others
    in your projects with Mozilla. We want to help you engage your
    community in a way that encourages contributors and builds other
    leaders.
 \end{quote}

>>>>

Mozilla Science maintains a ``Working Open Project Guide''~\cite{working-open-wssspe3}, the introduction of which states:
\begin{quote}
Working openly with contributors enables your
    community to learn how to build and collaborate together. This
    document is a guideline on how to work openly and involve others
    in your projects with Mozilla. We want to help you engage your
    community in a way that encourages contributors and builds other
    leaders.
 \end{quote}
